A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-20 FMCAD2021/paper.tex
opt section
update sec 4
preliminaries
flattening section
section 3
normalization
section 4
sec6 half done
intro add optimization part
section 3 and 4
abstract

% !TEX program = xelatex
%
\documentclass[10pt,letterpaper]{IEEEtran}

@@

\usepackage{graphicx}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{times} 
\usepackage{tikz}
\usetikzlibrary{automata, positioning, arrows}
\tikzset{
->, % makes the edges directed
>=stealth, % makes the arrow heads bold
node distance=2cm, % specifies the minimum distance between two nodes. Change if necessary.
every state/.style={thick, fill=gray!10}, % sets the properties for each ’state’ node
initial text=$ $, % sets the text that appears on the start arrow
}

\RequirePackage{todonotes}
\newcommand{\znjSide}[1]{\todo[color=orange!10]{\textbf{ZHAN:} #1}}
\newcommand\znj[1]{\textcolor{red}{#1}}
\newcommand{\parseInt}{\textsf{parseInt}}
\newcommand{\paexp}{$\textsf{PA}_{\exp}$}
\newcommand{\Def}{\hat{=}}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{resume}{Resume}
%\newtheorem{claim}{Claim}

@@

@@

\begin{abstract}
    String constraint solving is the core of various testing and verification approaches for scripting languages. 
    Among algorithms for solving string constraints, flattening is a well-known approach that is particularly useful in handling satisfiable instances.
    In the PLDI 2020 paper of Abdulla et al., the authors extended the flattening approach to support the string-integer conversion, which is an important function appearing in almost all scripting languages.
    However, their approach supports only a special flattening pattern and leaves the support of the general flat regular constraints as an open problem.
    In this paper, we fill the gap and propose a complete flattening approach for the string-integer conversion. The approach is built upon a decision procedure for the linear-exponential arithmetic constraints (namely, the extension of Presburger arithmetic with exponential functions) proposed by Point in 1986. While the decision procedure by Point relies on quantifier eliminations and is expensive, we introduce various optimizations and provide an efficient implementation.
%    Besides the theoretical results, we also develop various optimizations and provide an implementation.
    We evaluate the performance of the implementation on the benchmarks that are generated from the string hash functions as well as randomly.
    The experimental results show that our implementation outperforms the state-of-the-art solvers for string-integer conversion constraints as well as linear-exponential constraints, in both precision and efficiency.
%\keywords{ String-integer conversion \and Flat regular constraints \and Presburger arithmetic \and Exponential function \and Quantifier elimination.}

@@

\section{Decision procedure for $(\mathbb{N},+,2^x)$}

@@

\section{Optimizations}

@@

\section{Implementation and Experiments}

@@

%test bib
\bibliographystyle{plain}
\bibliography{reference}

>>>>

% !TEX program = pdflatex
%
\documentclass[10pt,letterpaper]{IEEEtran}

@@

\usepackage{graphicx}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{times} 
\usepackage{tikz}
\usepackage{multirow}

\usetikzlibrary{automata, positioning, arrows}
\tikzset{
->, % makes the edges directed
>=stealth, % makes the arrow heads bold
node distance=2cm, % specifies the minimum distance between two nodes. Change if necessary.
every state/.style={thick, fill=gray!10}, % sets the properties for each ’state’ node
initial text=$ $, % sets the text that appears on the start arrow
}

\RequirePackage{todonotes}
\newcommand{\parseInt}{\textsf{parseInt}}
\newcommand{\pa}{{\sf PA}}
\newcommand{\qfpa}{{\sf QFPA}}
\newcommand{\paexp}{{\sf ExpPA}}
\newcommand{\Def}{\hat{=}}
\newcommand{\strint}{{\sf STR}_\parseInt}

\newcommand{\Nat}{\mathbb{N}}
\newcommand{\Int}{\mathbb{Z}}
\newcommand\Aut{\mathcal{A}}
\newcommand\Lang{\mathcal{L}}
\newcommand\free{\mathrm{Free}}
\newcommand\op{\odot}
\newcommand\parikh{\mathbb{P}}
\newcommand{\hide}[1]{}
\newcommand\encode{\mathit{encode}}
\newcommand\decode{\mathit{decode}}
\newcommand\len{\textsf{len}}
\newcommand\svars{\mathcal{X}}
\newcommand\ivars{\mathbbm{X}}
\newcommand\pos{\mathit{pos}}
\newcommand\ltrue{\mathtt{true}}
\newcommand\lfalse{\mathtt{false}}
\newcommand\flatdom{\mathcal{R}}
\newcommand\flatten{\mathit{flatten}}
\newcommand\svarx{x}
\newcommand\svary{y}
\newcommand\ivarx{\mathbbm{x}}
\newcommand\ivary{\mathbbm{y}}
\newcommand\ivarz{\mathbbm{z}}
%\newcommand\notsubstr{\tt{NotSubstr}}
\newcommand\concat{\cdot}
\newcommand\sterm{t}
\newcommand\iterm{\mathbbm{t}}
\newcommand{\kell}{{(k,\ell)}}

\newcommand{\svar}{\textsf{SVar}}
\newcommand{\ivar}{\textsf{IVar}}
\newcommand{\pvar}{\textsf{PVar}}
\newcommand{\flatfun}{\mathcal{F}}

\usepackage{bbm}
\usepackage{amsthm}
\usepackage{stmaryrd}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{resume}{Resume}
%\newtheorem{claim}{Claim}

@@

\newcommand{\znj}[1]{\color{red} {NJ: #1 :JN} \color{black}}
\newcommand{\znjSide}[1]{\todo[color=orange!10]{\textbf{ZHAN:} #1}}
\newcommand{\zhilin}[1]{\color{brown} {ZL: #1 :LZ} \color{black}}
\newcommand{\wuhao}[1]{\color{cyan} {WH: #1 :HW} \color{black}}
\newcommand{\yfc}[1]{\color{violet} {YF: #1 :FY} \color{black}}

@@

\begin{abstract}
    String constraint solving is the core of various testing and verification approaches for scripting languages. 
    Among algorithms for solving string constraints, flattening is a well-known approach that is particularly useful in handling satisfiable instances.
    As string-integer conversion is an important function appearing in almost all scripting languages, Abdulla et al. extended the flattening approach to this function recently.
    However, their approach supports only a special flattening pattern and leaves the support of the general flat regular constraints as an open problem.
    In this paper, we fill the gap and propose a complete flattening approach for the string-integer conversion. The approach is built upon a quantifier elimination procedure for the linear-exponential arithmetic constraints (namely, the extension of Presburger arithmetic with exponential functions) proposed by Point in 1986. While the quantifier elimination procedure by Point is too expensive to be implemented efficiently, we propose various optimizations and provide an efficient implementation.
%    Besides the theoretical results, we also develop various optimizations and provide an implementation.
    We evaluate the performance of our implementation on the benchmarks that are generated from the string hash functions as well as randomly.
    The experimental results show that our implementation outperforms the state-of-the-art solvers. 
    %for string-integer conversion as well as linear-exponential constraints.
    %, in both precision and efficiency.     
%\keywords{ String-integer conversion \and Flat regular constraints \and Presburger arithmetic \and Exponential function \and Quantifier elimination.}

@@

\section{Decision procedure for {\paexp}}\label{sec-dec}

@@

\section{Optimizations}\label{sec-opt}

@@

\section{Implementation and Experiments}\label{sec-exp}

@@

\newpage

%test bib
\bibliographystyle{plain}

\bibliography{reference}

\newpage

\begin{appendix}

\input{8_appendix.tex}

\end{appendix}
